Persistence of marine populations under climate and fishing

### 2014-03-03 Writing/MS.tex

When the climate changes, so does the location of habitats suitable for an organism's survival and reproduction. This change does not occur in isolation but rather appears on a background of other disturbances, making the study of interactions between stressors important. In order to understand how two disturbances, range shift and harvesting, interact and affect population persistence, we analyzed an integrodifference model that explicitly included the mechanisms of dispersal and reproduction. We found how the critical rates of harvesting and climate velocity depend on the growth rate and dispersal kernel of the population.  We measured the interaction between the stressors and found that the disturbances interact nearly additively, with low positive synergy only at the greatest harvest rates and climate velocity that almost drive the population extinct. We also introduced two conservation techniques into simulations of the population model --- threshold harvest rules and marine protected areas (MPAs) --- and found that under some circumstances these approaches could be effective management tools as they mitigate the interaction between the two stressors.  
\hspace{10cm}

@@

Many stressors can disturb an ecosystem, and ecologists have quantified the consequences of a great deal of these of perturbations \citep{Wilcoveetal1998, Crainetal2008, DarlingCote2008}. Less work, however, has been done to measure the effects of multiple stressors and the interactions between them.  If disturbances interact synergistically, a perturbation that has little effect when it occurs individually may amplify the disturbance caused by a coincident perturbation \citep{Crainetal2008, DarlingCote2008,Nyeetal2013,Gurevitchetal2000}.   In the most extreme (and worrying) cases, synergistic interactions between multiple stressors will drive a population extinct even though it could persist in the face of any single stressor (e.g. \citet{Pelletieretal2006}).  If disturbances interact antagonistically, on the other hand, the effects of multiple stressors may be less than that predicted by the individual effects of the stressors.  Since disturbances rarely occur in isolation, measuring the effects of multiple disturbances gives a better understanding of the likely impacts to the system \citep{DoakMorris2010, Fordhametal2013, Foltetal1999}.

Climate change and fishing, two of the largest human impacts on the ocean \citep{Halpernetal2008}, provide an important case study of how disturbances interact in their effects on biological populations.  Marine fish are already moving in response to climate change \citep{Perryetal2005, HiddinkHoftstede2008, Rijnsdorpetal2009, Dulvyetal2008, Simpsonetal2011} and are projected to continue in the future \citep{Kelletal2005, Mackenzieetal2007}. These shifting species, and those likely to move in the future, are also subject to harvesting, among other disturbances including pollution, ocean acidification, habitat fragmentation, and invasive species \citep{Wilcoveetal1998, Salaetal2000, MEA2005, Pinskyetal2013, Barryetal1995, Nyeetal2009}. Previous empirical work has found synergistic interactions between overfishing and temperature-driven range shifts \citep{Lingetal2009} and microcosm experiments have identified synergistic interactions between warming temperatures, harvesting and connectivity \citep{Moraetal2007}. This empirical work underscores the importance of understanding how range shifts and harvesting interact.

A common approach to predicting future population distributions has been to use bioclimatic-envelope models (also known as species distribution models -- SDMs). These statistical models typically correlate presence-absence data with biophysical characteristics such as mean or maximum temperatures, rainfall, or salinity, to predict how species ranges' will differ under climate change \citep{Elithetal2006, GuisanThuiller2005, GuisanZimmerman2000}. Despite these models' widespread adoption, many papers have criticized SDMs as oversimplified as they lack species interactions, dispersal and reproductive processes \citep{KearneyPorter2009, Zarnetskeetal2012, Robinsonetal2011}.  Recent work on range shifts has addressed some of these gaps by explicitly including dispersal and reproduction \citep{Berestyckietal2009, ZhouKot2011}. However these models only address one disturbance, climate-driven range shifts.

@@

We studied the dynamics of a fish population constrained to a single, one-dimensional habitat patch by their inability to reproduce outside of that area as introduced by \cite{ZhouKot2011}. This viable habitat patch (here after `patch') shifts at a fixed velocity and harvest occurs at each point in space along the entire one-dimensional world.  We first determined the climate velocity and harvesting rate that would drive the population extinct (hereafter the critical harvesting rate and climate velocity), and then measured synergy by calculating the drop in biomass caused by each stressor both individually and together. We finally add marine protected areas (MPAs) and threshold harvesting rules in numerical simulations of the model to determine how these management strategies affect population persistence.

@@

In the model of \cite{ZhouKot2011}, the adults from the current year produce offspring according to a recruitment function and these offspring disperse across the one-dimensional world according to a dispersal kernel to become the next generation's adults.  We extend this model by additionally subjecting the adults to harvesting before they produce offspring so that only a proportion of the fish survive to reproduce. We incorporate these processes-- recruitment, harvesting, and dispersal-- into an integrodifference model to describe how the population changes over time. If $n_t(x)$ 
is the density of fish at position $x$ at time $t$, then the density of fish at the next generation is given by

@@

\noindent where $h$ is the proportion of adults harvested, $f(n)$ is the recruitment function giving the number of 
offspring produced by a population of size $n$ (accounting for density dependence), $k(x-y)$ is the dispersal kernel giving the probability of a  larva traveling from position $y$ to position $x$, $L$ is the length of the patch, and $c$ is the rate at which it  shifts across space.  We provide a list of variables and functions in Table \ref{variables}.  We use a Beverton-Holt recruitment function,

\[f(n_t)=\frac{R_0n_t}{1+\left(\frac{R_0-1}{K}\right)n_t}\]

\noindent but regardless of the exact functional form of the recruitment function, the critical parameter in determining population persistence is how quickly recruitment increases when the population size is near (but above) $0$, which is equivalent to the intrinsic growth rate $R_0=f'(0)$.  Analyzing this kind of model becomes easier if the dispersal kernel is separable into its dependence on the source of larvae and its dependence on the destination of the larvae, i.e.~if there are functions $a_i, b_i$ such that $k(x- y) = \sum^\infty_{i=1} a_i(x)b_i(y)$.  In our analyses, as in \cite{Latore:1998fk}, we used the separable Gaussian kernel given by

@@

\noindent To derive analytical expressions, we approximated the kernel, as described in the Appendix. %section number necessary?
Analytical results for a separable sinusoidal kernel are also described in the Appendix.  %awkward
We used simulations to analyze a Laplace dispersal kernel that is not amenable to this method, as described below.  % Why did we choose a Laplace dispersal kernel for simulations?

At equilibrium, a traveling wave will describe the population, where the density of fish at a given point in space will change but the density of fish at a location relative to the shifting patch will not. We sought to describe  the distribution of the population over the viable patch as it shifts through the world in order to study the size of the population at equilibrium and whether or not the population could persist. The traveling wave $n^*$ must satisfy

@@

\noindent where $\bar{x}\in\left[-\frac{L}{2}, \frac{L}{2}\right]$ describes the position within the patch \citep{ZhouKot2011}.

\subsection{Persistence }
One possible equilibrium traveling wave that solves Equation (\ref{traveling_pulse}) is the `trivial' traveling pulse, $n^*(\bar{x}) = 0$ for all $x \in \left[-\frac{L}{2}, \frac{L}{2}\right]$, i.e.~a patch with no fish in it.  If a population persists, it must be able to avoid extinction and grow even when small. We can think of a small population as a perturbation to the trivial traveling pulse. If the trivial pulse is stable, the system will return to the trivial pulse even after the introduction of a small population. If the trivial pulse is unstable, a small population may increase and form a persistent population. Population persistence is therefore equivalent to the trivial traveling pulse being an unstable equilibrium.

If we harvest the population at low enough levels and the climate velocity is slow enough, the population will be able to persist.  There exists threshold values of the harvesting rate $h$ and a climate velocity $c$ such that if we increase parameters beyond these values, we drive the population extinct.  We found these critical parameters, $h^*$, and  $c^*$, by finding the parameters that make the trivial pulse unstable (See Appendix \ref{stab}).

For each kernel, the population's ability to persist depends on properties of the population itself-- the expected distance a larva disperses $\langle d \rangle$ and the intrinsic growth rate $R_0$; properties of the environment-- the length of the viable patch $L$ and how quickly the environment shifts $c$; and the harvesting rate $h$.  The population biomass at equilibrium depends on the function form of recruitment, but population persistence only depends on the intrinsic growth rate $R_0$.  For a Gaussian kernel, the critical rates $c^*$ and $h^*$ are those values of $c$ and $h$ such that

We derive a similar expression for a sinusoidal kernel in the Appendix [{\bf REF?}].  For both kernels, we can approximate the critical harvesting proportion by a function that looks like 
\begin{equation*}
h^*\sim1- \frac{1}{R_0}\cdot C(L,R_0)f(\langle d \rangle,c^2,L^2+3c^2),
\end{equation*}
where $C(L,R_0)$ is a decreasing function of the length of the viable patch and the intrinsic growth rate.

\citet{ZhouKot2011} only considered whether a shifting environment will drive a population extinct.   In order to quantify whether the two stressors interact additively, synergistically, or antagonistically, we found the total biomass of the population when it reached an equilibrium traveling pulse and compared this equilibrium biomass in the presence and absence of each stressor individually or the two stressors together.  For a separable kernel, the equilibrium traveling pulse $n^*(x)$ must satisfy

@@

\noindent \citep{Latore:1998fk}. Equation (\ref{recursive_m}) allowed us to find the values of $m_i$ numerically. We then found the total biomass in the 
equilibrium traveling pulse by using these $m_i$ and integrating Equation (\ref{separable_integrodifference}).

@@

\noindent If the stressors aggravate each other, synergy is positive, and the effect of both stressors is worse than would we expect from considering either stressor individually. If the stressors alleviate each other, the synergy is negative, and the effect of both stressors is better than we expecte from considering either stressor individually. If the effect of both stressors is exactly as expected from considering either stressor individually, there is no interaction and no synergy.

@@

\noindent a commonly used model of larval dispersal \citep{Pinsky:2011fk}.  Second, we examined harvesting rules more complex than harvesting a constant proportion of the population. Whereas population persistence in the analytical model does not depend on the functional form of recruitment $f$, to perform simulations we must specify a recruitment function.  Again, we chose to use a Beverton-Holt function.  In the first generation, we seeded the world with 50 individuals at a single point, as in \cite{ZhouKot2011}. We first ran through 150 generations in order for the population to reach equilibrium without harvesting or climate shift.  We then added harvesting pressure, allowed the population to again reach equilibrium (150 generations), and finally added climate change by moving the viable patch.  We calculate equilibrium biomass as the mean biomass of 300 time steps once the difference in biomass between time step $t$ and $t+1$ was no greater than $0.1$.

n, in order to confirm our analytical results, we first added harvesting pressure by harvesting a constant proportion of the population. We then evaluated the effect of a threshold harvest rule and marine protected areas (MPAs).  With a threshold rule, we evaluated the population at each point in space to determine how much harvesting should occur. If the population abundance was below the designated threshold, no harvesting occurred. If the population exceeded the threshold, then we harvested all the `surplus' individuals.

MPAs are a form of management designed to check the impact of fishing on targeted populations and are typically designed to meet either conservation of fishery management goals \citep{Agardy1994, HollandBrazee1996, Gainesetal2010a}. To implement an MPA management strategy in our model, we examine the effect of both of these commonly advocated approaches. While both conservation and fisheries oriented MPA schemes align in their goal of maintaining a sustainable fished population, they differ in desired level of adult spillover. Fisheries-oriented MPAs are often designed such that they maximize adult spillover into fishable areas by creating many small reserves closely spaced \citep{HastingsBotsford2003}. The converse of this is the goal of conservation-oriented MPAs which seek to reduce adult spillover by minizing the ratio between the reserve edge length relative to area protected \citep{Gainesetal2010a}.

We introduce networks of MPAs into our simulations by designating segments of space where the harvesting rate was equal to $0$. Conservation-oriented MPAs, are frequently large and rarely part of a larger network of reserves \citep{HastingsBotsford2003}. For solitary reserves to be successful at protecting target species, they must encompass self-sustaining fish populations \citep{HastingsBotsford2006, Gainesetal2010a}. As such modeling studies estimate that isolated reserves must be at least as large as the average dispersal distance for the targeted fish species \citep{Lockwoodetal2002, HastingsBotsford2003, Botsfordetal2001, Gainesetal2010}. To implement conservation MPAs we created reserves with a length of 4 times the average dispersal distance and had a distance of 8 times the average dispersal distance between them to ensure that populations would be self sustiaining and not dependent on other dispersal for other reserves \citep{Lockwoodetal2002}.

Previous work has shown that if MPAs are to benefit fisheries, the reserves should be broken into a network, closely spaced to maximize adult spillover into fishable areas and export of larvae from reserve to reserve \citep{ HastingsBotsford2003, Gaylordetal2005, Gainesetal2010a}. To mimic this management scheme, MPAs had a length of $\tfrac{1}{3}$ of the average dispersal distance and had a distance of $\tfrac{2}{3}$ of the average dispersal distance between them.

@@

\subsection{Interactions Between Stressors }
We find the critical climate velocity and harvest  rate to be inversely related: as the harvesting rate $h$ increases, the critical climate velocity $c^*$ decreases, as the environment must move more slowly to accommodate the population growing more slowly (Figure \ref{baseline}). % this seems like a backwards way to say it. Instead of "as the environment must move more slowly to accommodate..." it seems like it should be "as the population can only survive in increasingly stationary habitats".. But "increasingly stationary" is not great... Ideas?
Conversely, as the rate of environmental shift $c$ increases, the critical harvesting rate $h^*$ decreases (Figure  \ref{baseline}). This means that a harvesting rate that is sustainable in the absence of environmental shift may no longer be sustainable if the environment starts changing. When the climate velocity or harvesting pressure exceed their critical rates ($h^*, c^*$ respectively), the biomass of the population at equilibrium will be equal to $0$.  Before the stressors reaches those thresholds, the equilibrium biomass of the population decreases as either the harvesting pressure increases or the environmental shifts more quickly (Figure \ref{baseline}). Our simulations confirm the analytical results with the critical speed $c^*$ declining as the critical harvest rate $h^*$ increases and vice versa (Figure \ref{nomang}).

It is always the case that increasing the intrinsic growth rate, $R_0$, of the population increases the critical climate velocity $c^*$ and the critical harvesting rate $h^*$, since a population that grows more quickly can recover more quickly from losses caused by these disturbances. However, whether or not dispersing farther is better depends on how quickly the environment is shifting (Figure \ref{baseline}). When the environment is shifting slowly, dispersing farther is detrimental since many larvae will disperse too far away from the viable patch. When the environment is shifting quickly, on the other hand, dispersing farther can help the population persist because some larvae will disperse into the space that will become viable shortly in the future.  This affects the critical harvesting rate: at a low rate of environmental shift, we can more severely harvest populations that have a shorter dispersal distance than those that disperse farther, whereas at a high rate of environmental shift, we can more aggressively harvest populations that disperse farther.

We found low levels of positive synergy between the two stressors in our analysis of the Gaussian kernel (Figure \ref{Synergy}).  Where positive synergy exists, a doubly stressed population loses more biomass than we would predict from either stressor individually.  The stressors interact most strongly at high values, shortly before they drive the population extinct.  However, the excess loss in biomass is low, making it difficult to distinguish positive synergy from additive interactions. % this is my awkward sentence, any ideas?
We found similar analytical results for a sinusoidal dispersal kernel, which indicates that this result is robust to changes in the dispersal kernel.

@@

Without any management strategies, we found that the more severely we harvest the population, the slower the rate of environmental shift will suffice to drive the population extinct. However, when we put thresholds in place, a small population can always escape harvesting pressure and the critical rate of environmental shift $c^*$ no longer depends on the harvesting rate (Figure \ref{management}). In other words, as long as there is some threshold below which harvesting is not allowed, there is a constant critical rate of environmental shift that only depends on the growth rate, length of the viable patch, and average dispersal distance.

We also examined the effect of marine protected  areas (MPAs) on the population's persistence to see whether it might extend the range of harvesting and  climate change parameters where the fish population could survive. We found that with either type of MPA strategies examined (many small versus few large), the population withstood combinations of higher climate velocities and harvesting rates, although the critical climate velocity $c^*$ was unchanged (Figure \ref{management}). We also found that the spacing and size of the MPAs changed population dynamics. MPAs spaced more than one average dispersal distance apart resulted in large oscillations of population biomass at low climate velocities relative to small, closely spaced, MPAs. For both of these MPA strategies we find that as climate velocities increase, the mean population abundance declines but the population experiences less extreme oscillations in abundance, which results in a population bounded farther from possible extinction in a stochastic environment. Additionally, large MPAs were able to increase equilibrium biomass under relatively high harvest and intermediate speeds relative to a population harvested at the same rate, but at a slower speed. This effect disappears at faster climate velocities and is not present in the other, many-small MPA, strategy we tested.

@@

For each kernel we studied, we found that the higher the growth rate and the better the mean dispersal distance matches the rate of environmental shift, the better a population can adjust to harvest and climate change.  More interestingly, we found a negative relationship between the critical harvesting rate and the rate of environmental shift.  That is, the more quickly the environment shifts the less harvesting it takes to drive the population extinct.  This is an indication of an interaction between the stressors.

@@

Our results suggest that particular combinations of harvesting and rate of environmental shift will affect some species more than others. As shown in Figure \ref{baseline}, species with a higher reproductive rate and a longer average dispersal distance will better track a high rate of environmental shift relative to a species that has a low reproductive rate and short dispersal distance. The finding that a higher reproductive rate can sustain higher climate velocities and harvesting rates is intuitive, especially because harvesting rate and reproductive rate cancel each other out. However it is worth pointing out that a higher reproductive rate can be generated either by shorter generation times or higher fecundity. Finding that species with shorter generation times can better keep up with shifts in climate is in agreement with empirical work which has found that fish which shifted in response to warming in North Sea had faster life histories than non shifting species \citep{Perryetal2005}. While higher reproductive rates improved a population's ability to persist, there was a tradeoff in increasing dispersal distances. At low speeds, we found that a short dispersal dispersal distance improved the maximum harvesting rate a population could sustain while at higher speeds a longer dispersal distance improved the maximum climate velocity in which the population could persist (Figure \ref{baseline}). This tradeoff is due to the proportion of dispersing  offspring at time step $t$ which lands within the patch at time step $t + 1$. When climate is shifting slowly, a large dispersal distance sends most offspring ahead of the patch, while with faster climate velocities a long dispersal distance allows the population to make it to the new patch (Figure \ref{baseline}). Thus climate velocity will selectively favor species with dispersal distances best matched to the rate of shift.

@@

\noindent {\bf Figure \ref{baseline}}: (a) The critical harvesting rate on the y-axis as a function of the rate of environmental shift on the x-axis.  Black lines correspond to a growth rate of $R_0=3$, red to $R_0=7$, and blue to $R_0=10$.  Solid lines correspond to an average dispersal distance $\langle d \rangle =0.1$ and dashed lines correspond to an average dispersal distance $\langle d \rangle =0.25$.  These results are from an approximated Gaussian dispersal kernel with $L=1$.  (b) 
The equilibrium biomass of the population as a function of the rate of environmental shift on the x-axis and the harvesting rate on the y-axis. These results are from a Gaussian dispersal kernel with parameters $L=1$, $R_0=5$, $\langle d \rangle = 0.399$. 
\hspace{6in}
\hspace{6in}

>>>>

When the climate changes, so does the location of habitats suitable for an organism's survival and reproduction. This change does not occur in isolation but rather appears on a background of other disturbances, making the study of interactions between stressors important. In order to understand how two disturbances, range shift and harvesting, interact and affect population persistence, we analyzed an integrodifference model that explicitly included the mechanisms of dispersal and reproduction. We found how the critical rates of harvesting and climate velocity that suffice to drive the population extinct depend on the growth rate and dispersal kernel of the population.  We measured the interaction between the stressors and found that the disturbances interact nearly additively, with low positive synergy only at the greatest harvest rates and climate velocity that almost drive the population extinct. We also introduced two conservation techniques into simulations of the population model, threshold harvest rules and marine protected areas (MPAs), and found that under some circumstances these approaches could be effective management tools as they mitigate the interaction between the two stressors.  
\hspace{10cm}

@@

Many stressors can disturb an ecosystem, and ecologists have quantified the consequences of many of these of perturbations \citep{Wilcoveetal1998, Crainetal2008, DarlingCote2008}. Less work, however, has been done to measure the effects of multiple stressors and the interactions between them.  If disturbances interact synergistically, a perturbation that has little effect when it occurs individually may amplify the disturbance caused by a coincident perturbation \citep{Crainetal2008, DarlingCote2008,Nyeetal2013,Gurevitchetal2000}.   In the most extreme (and worrying) cases, synergistic interactions between multiple stressors will drive a population extinct even though it could persist in the face of any single stressor (e.g. \citet{Pelletieretal2006}).  If disturbances interact antagonistically, on the other hand, the effects of multiple stressors may be less than that predicted by the individual effects of the stressors.  Since disturbances rarely occur in isolation, measuring the effects of multiple disturbances gives a better understanding of the likely impacts to the system \citep{DoakMorris2010, Fordhametal2013, Foltetal1999}.

Climate change and fishing, two of the largest human impacts on the ocean \citep{Halpernetal2008}, provide an important case study of how disturbances interact in their effects on biological populations.  Marine fish are already moving in response to climate change \citep{Perryetal2005, HiddinkHoftstede2008, Rijnsdorpetal2009, Dulvyetal2008, Simpsonetal2011} and are projected to continue in the future \citep{Kelletal2005, Mackenzieetal2007}. These shifting species, and those likely to move in the future, are also subject to harvesting, among other disturbances including pollution, ocean acidification, habitat fragmentation, and invasive species \citep{Wilcoveetal1998, Salaetal2000, MEA2005, Pinskyetal2013, Barryetal1995, Nyeetal2009}. Previous empirical work has found synergistic interactions between overfishing and temperature-driven range shifts \citep{Lingetal2009} and synergistic interactions between warming temperatures, harvesting and connectivity have been identified in microcosm experiments \citep{Moraetal2007}. This empirical work underscores the importance of understanding how range shifts and harvesting interact.

A common approach to predicting future population distributions has been to use bioclimatic-envelope models (also known as species distribution models -- SDMs). These statistical models typically correlate presence-absence data with biophysical characteristics such as mean or maximum temperature, rainfall, or salinity, to predict how species ranges' will differ under climate change \citep{Elithetal2006, GuisanThuiller2005, GuisanZimmerman2000}. Despite these models' widespread adoption, many papers have criticized SDMs as oversimplified as they lack species interactions, dispersal and reproductive processes \citep{KearneyPorter2009, Zarnetskeetal2012, Robinsonetal2011}.  Recent work on range shifts has addressed some of these gaps by explicitly including dispersal and reproduction \citep{Berestyckietal2009, ZhouKot2011}. However these models only address one disturbance, climate-driven range shifts.

@@

We studied a model of the dynamics of a fish population constrained to a single, one-dimensional habitat patch by their inability to reproduce outside of that area, as introduced by \cite{ZhouKot2011}. This viable habitat patch (here after `patch') shifts at a fixed velocity and harvest occurs at each point in space along the entire one-dimensional world.  We first determined the harvesting rate climate velocity that would drive the population extinct (hereafter the critical harvesting rate and critical climate velocity), and then measured synergy by calculating the drop in biomass caused by each stressor both individually and together. We finally added threshold harvesting rules and marine protected areas (MPAs) in numerical simulations of the model to determine how these management strategies affect population persistence.

@@

In the model of \cite{ZhouKot2011}, the adults from the current year produce offspring according to a recruitment function and these offspring disperse across the one-dimensional world according to a dispersal kernel to become the next generation's adults.  We extend this model by additionally subjecting the adults to harvesting before they produce offspring so that only a proportion of the fish survive to reproduce. These processes-- recruitment, harvesting, and dispersal-- are incorporated into an integrodifference model to describe how the population changes over time. If $n_t(x)$ 
is the density of fish at position $x$ at time $t$, then the density of fish at the next generation is given by

@@

\noindent where $h$ is the proportion of adults harvested, $f(n)$ is the recruitment function giving the number of 
offspring produced by a population of size $n$ (accounting for density dependence), $k(x-y)$ is the dispersal kernel giving the probability of a  larva traveling from position $y$ to position $x$, $L$ is the length of the patch, and $c$ is the rate at which it  shifts across space.  We provide a list of variables and functions in Table \ref{variables}.  We used a Beverton-Holt recruitment function,

\[f(n_t)=\frac{R_0n_t}{1+\left(\frac{R_0-1}{K}\right)n_t}.\]

\noindent  Analyzing this kind of model becomes easier if the dispersal kernel is separable into its dependence on the source of larvae and its dependence on the destination of the larvae, i.e.~if there are functions $a_i, b_i$ such that $k(x- y) = \sum^\infty_{i=1} a_i(x)b_i(y)$.  In our analyses, as in \cite{Latore:1998fk}, we used the separable Gaussian kernel given by

@@

\noindent To derive analytical expressions, we approximated the kernel, as described Appendix A.3.
Analytical results for a separable sinusoidal kernel are also described in Appendix A.4.  
We used simulations to analyze a Laplace dispersal kernel that is not amenable to this method, as described below.

At equilibrium, the population will move in a traveling wave, where the density of fish at a given point in space will change but the density of fish at a location relative to the shifting patch will not. The traveling wave $n^*$ must satisfy

@@

\noindent where $\bar{x}\in\left[-\frac{L}{2}, \frac{L}{2}\right]$ describes the position within the patch \citep{ZhouKot2011}. For a separable kernel, the equilibrium traveling pulse $n^*(x)$ must satisfy

@@

\noindent \citep{Latore:1998fk}.

\subsection{Persistence }
If the population is harvested at low enough levels and the climate velocity is slow enough, the population will be able to persist.  There are threshold values of the harvesting rate $h$ and the climate velocity $c$ such that if we increase the parameters beyond these values, the population will be driven extinct.  When the population is extinct, the system is in equilibrium, i.e. there is a `trivial' traveling pulse, $n^*(\bar{x}) = 0$ for all $x \in \left[-\frac{L}{2}, \frac{L}{2}\right]$, which satisfies Equation (\ref{traveling_pulse}).  If a population persists, it must be able to avoid extinction and grow even when small. If the trivial pulse is stable, the system will return to extinction even after the introduction of a small population. If the trivial pulse is unstable, a small population may increase and form a persistent population. Population persistence is therefore equivalent to the trivial traveling pulse being an unstable equilibrium.  We found the critical parameters, $h^*$ and  $c^*$, by finding the parameters that make the trivial pulse unstable.  See Appendix A.1 for details.

Regardless of the exact functional form of the recruitment function, the critical parameter in determining population persistence is how quickly recruitment increases when the population size is near (but above) $0$, which is equivalent to the intrinsic growth rate $R_0=f'(0)$.  For each kernel, the population's ability to persist depends on properties of the population itself-- the expected distance a larva disperses $\langle d \rangle$ and the intrinsic growth rate $R_0$; properties of the environment-- the length of the viable patch $L$ and how quickly the environment shifts $c$; and the harvesting rate $h$.  For a Gaussian kernel, the critical rates $c^*$ and $h^*$ are those values of $c$ and $h$ such that

We derive a similar expression for a sinusoidal kernel in the Appendix A.4.  For both kernels, we can approximate the critical harvesting proportion by a function that looks like 
\begin{equation*}
h^*\sim1- \frac{1}{R_0}\cdot C(L,R_0)f(\langle d \rangle,c^2,L^2+3c^2),
\end{equation*}
where $C(L,R_0)$ is a decreasing function of the length of the viable patch and the intrinsic growth rate.

\citet{ZhouKot2011} only considered whether a shifting environment will drive a population extinct.   In order to quantify whether the two stressors interact additively, synergistically, or antagonistically, we found the total biomass of the population when it reached an equilibrium traveling pulse and compared this equilibrium biomass in the presence and absence of each stressor individually or the two stressors together.   Equations (\ref{recursive_m}) and (\ref{separable_integrodifference}) allowed us to numerically find the  total biomass in the equilibrium traveling pulse.

@@

\noindent If the stressors aggravate each other, the effect of both stressors is greater than  we would expect from considering either stressor individually and synergy is positive. If the stressors alleviate each other, the effect of both stressors is less than we would expect from considering either stressor individually and synergy is negative. If the effect of both stressors is exactly as expected from considering either stressor individually, there is no interaction and no synergy.

@@

\noindent a commonly used model of larval dispersal \citep{Pinsky:2011fk}.  Second, we implemented two management strategies, threshold rules and MPAs, to understand their effect on population persistence and on the synergistic interactions between stressors.  For every simulation, in the first generation, we seeded the world with 50 individuals at a single point, as in \cite{ZhouKot2011}. We first ran through 150 generations in order for the population to reach equilibrium without harvesting or climate shift.  We then added harvesting pressure, allowed the population to again reach equilibrium (150 generations), and finally added climate change by moving the viable patch.  We calculated equilibrium biomass as the mean biomass of 300 time steps once the difference in biomass between successive generations was no greater than $0.1$.

Under the two management strategies, harvesting pressure was implemented differently.  With a threshold rule, we evaluated the population at each point in space to determine how much harvesting should occur. If the population abundance was below the designated threshold, no harvesting occurred. If the population exceeded the threshold, then we harvested all the `surplus' individuals.

We introduce networks of MPAs into our simulations by designating segments of space where the harvesting rate was equal to $0$.  MPAs are typically designed to meet either fishery management  or conservation goals \citep{Agardy1994, HollandBrazee1996, Gainesetal2010a}.  Fisheries-oriented MPAs are often designed such that they maximize adult spillover into fishable areas by creating many small reserves closely spaced \citep{HastingsBotsford2003,Gaylordetal2005, Gainesetal2010a}. To mimic this management scheme, we implemented MPAs with a length of $\tfrac{1}{3}$ of the average dispersal distance and a distance of $\tfrac{2}{3}$ of the average dispersal distance between them.   Conservation-oriented MPAs seek to reduce adult spillover by creating fewer larger protected areas \citep{HastingsBotsford2006, Gainesetal2010a}.  To mimic this scheme. we implemented MPAs with a length of $4$ times the average dispersal distance and a distance of $8$ times the average dispersal distance between them \citep{Lockwoodetal2002}.

@@

\subsection{Interactions Between Stressors }
The critical climate velocity and harvest  rate are inversely related.  As the climate velocity shift $c$ increases, the critical harvesting rate $h^*$ decreases (Figure  \ref{baseline}). This means that a harvesting rate that is sustainable in the absence of environmental shift may no longer be sustainable if the environment starts changing. Conversely, as the harvesting rate $h$ increases, the critical climate velocity $c^*$ decreases (Figure \ref{baseline}).  This means that as harvesting pressure increases, it becomes increasingly easy for a shifting environment to drive the population extinct.

When the climate velocity or harvesting pressure exceed their critical rates ($c^*, h^*$ respectively), the biomass of the population at equilibrium will be equal to $0$.  Before the stressors reaches those thresholds, the equilibrium biomass of the population decreases as either the harvesting pressure increases or the environmental shifts more quickly (Figure \ref{baseline}). Our simulations confirm the analytical results with the critical speed $c^*$ declining as the critical harvest rate $h^*$ increases and vice versa (Figure \ref{nomang}).

It is always the case that increasing the intrinsic growth rate, $R_0$, increases the critical climate velocity $c^*$ and the critical harvesting rate $h^*$, since a population that grows more quickly can recover more quickly from losses caused by these disturbances. However, whether or not dispersing farther is better depends on how quickly the environment is shifting (Figure \ref{baseline}). When the environment is shifting slowly, dispersing farther is detrimental since many larvae will disperse too far away from the viable patch. When the environment is shifting quickly, on the other hand, dispersing farther can help the population persist because some larvae will disperse into the space that will become viable shortly in the future.  This affects the critical harvesting rate: at a low climate velocity, we can more severely harvest populations that have a shorter dispersal distance than those that disperse farther, whereas at a high climate velocity, we can more aggressively harvest populations that disperse farther.

We found low levels of positive synergy between the two stressors in our analysis of the Gaussian kernel (Figure \ref{Synergy}).  Where positive synergy exists, a doubly stressed population loses more biomass than we would predict from either stressor individually.  The stressors interact most strongly at high values, shortly before they drive the population extinct.  However, the excess loss in biomass is very low, meaning the stressors interact more or less additively.  We found similar analytical results for a sinusoidal dispersal kernel, which indicates that this result is robust to changes in the dispersal kernel.

@@

Without any management strategies, we found that the more severely we harvest the population, a slower climate velocity will suffice to drive the population extinct. However, when we put thresholds in place, a small population can always escape harvesting pressure and the critical climate velocity $c^*$ no longer depends on the harvesting rate (Figure \ref{management}). In other words, as long as there is some threshold below which harvesting is not allowed, there is a constant critical climate velocity that only depends on the growth rate, length of the viable patch, and average dispersal distance.

With either type of MPA strategies examined (many small versus few large), the population withstood combinations of higher climate velocities and harvesting rates (Figure \ref{management}).  At lower climate velocities, MPAs spaced more than one average dispersal distance apart resulted in larger fluctuations of population biomass relative to small, closely spaced, MPAs.  As climate velocities increase, for both MPA strategies, the mean population abundance declines but the population experiences less extreme oscillations in abundance.  Since minimum population biomass is increased, the population would be more buffered from possible extinction in a stochastic environment. %Additionally, large MPAs were able to increase equilibrium biomass under relatively high harvest and intermediate speeds relative to a population harvested at the same rate, but at a slower speed. This effect disappears at faster climate velocities and is not present in the other, many-small MPA, strategy we tested. 
%I don't quite follow what I commented out above. -Eleanor

@@

For each kernel we studied, we found that the higher the growth rate and the better the mean dispersal distance matches the climate velocity, the better a population can adjust to harvest and climate change.  More interestingly, we found a negative relationship between the critical harvesting rate and the climate velocity.  That is, the more quickly the environment shifts the less harvesting it takes to drive the population extinct.  This is an indication of an interaction between the stressors.

@@

Our results suggest that particular combinations of harvesting and climate velocity will affect some species more than others. As shown in Figure \ref{baseline}, species with a higher reproductive rate and a longer average dispersal distance will better track a high climate velocity relative to a species that has a low reproductive rate and short dispersal distance. The finding that a higher reproductive rate can sustain higher climate velocities and harvesting rates is intuitive, especially because harvesting rate and reproductive rate cancel each other out. However it is worth pointing out that a higher reproductive rate can be generated either by shorter generation times or higher fecundity. Finding that species with shorter generation times can better keep up with shifts in climate is in agreement with empirical work which has found that fish which shifted in response to warming in North Sea had faster life histories than non shifting species \citep{Perryetal2005}. While higher reproductive rates improved a population's ability to persist, there was a tradeoff in increasing dispersal distances. At low speeds, we found that a short dispersal dispersal distance improved the maximum harvesting rate a population could sustain while at higher speeds a longer dispersal distance improved the maximum climate velocity in which the population could persist (Figure \ref{baseline}). This tradeoff is due to the proportion of dispersing  offspring at time step $t$ which lands within the patch at time step $t + 1$. When climate is shifting slowly, a large dispersal distance sends most offspring ahead of the patch, while with faster climate velocities a long dispersal distance allows the population to make it to the new patch (Figure \ref{baseline}). Thus climate velocity will selectively favor species with dispersal distances best matched to the rate of shift.

@@

\noindent {\bf Figure \ref{baseline}}: (a) The critical harvesting rate on the y-axis as a function of the climate velocity on the x-axis.  Black lines correspond to a growth rate of $R_0=3$, red to $R_0=7$, and blue to $R_0=10$.  Solid lines correspond to an average dispersal distance $\langle d \rangle =0.1$ and dashed lines correspond to an average dispersal distance $\langle d \rangle =0.25$.  These results are from an approximated Gaussian dispersal kernel with $L=1$.  (b) 
The equilibrium biomass of the population as a function of the climate velocity on the x-axis and the harvesting rate on the y-axis. These results are from a Gaussian dispersal kernel with parameters $L=1$, $R_0=5$, $\langle d \rangle = 0.399$. 
\hspace{6in}
\hspace{6in}

\noindent {\bf Figure \ref{Synergy}}: Positive synergy between the two stressors.  The x-axis shows the climate velocity, the y-axis shows the harvesting rate, and the color indicates the loss in biomass in the doubly stressed population in excess of the sum of the losses caused by each stressor individually, $E_\text{hc}-E_\text{h}-E_\text{c}$.  This excess loss, on the order of $.001$, is small in comparison to the total biomass, which can be as large as $20$.  These results are from an approximated Gaussian dispersal kernel with parameters $L=1$, $R_0=5$, $\langle d \rangle = 0.399$.
\hspace{6in}
\hspace{6in}
